\LARGE \bf Continuous Correlated Beta Processes for 3D Grasp Planning Under Uncertainty \versionline{1}

### 2015-07-27 ICRA2016/bandits_docs/includes/background.tex
Updated the correlated bandits paper with detailed related work, references, a revised intro problem statement, and background, and added some todos. Long way to go

We use Continuous Correlated Beta Processes (CCBPs) to model correlations in the probability of force closure between two grasps.
For example, two grasps that contact the shape in similar locations may have similar probabilities of force closure.
We refer the reader to Goetschalckx et al.~\cite{} for a detaled description of CCBPs.

@@

Consider a set of $K$ grasps $\Gamma = \{g_k\}_{k=1}^K$.
Then force closure for each grasp $F(g_k) \in \{0, 1\}$ is a Bernoulli random variable with probability of success $\theta_k = P_F(g_k)$.
Since we do not know the value of $\theta_k$ for each grasp, we can specify a distribution of $\theta_k$ based on our prior belief about the likelihood of force closure.
A common choice for a prior on the Bernoulli parameter $\theta_k$ is the Beta distribution, which is specified by shape parameters $\alpha > 0$ and $\beta > 0$:

@@

\begin{align*}
	\mathbb{E} \left[ \theta_k | F_{1}(g_k), ..., F_{t}(g_k) \right] = \frac{\alpha_{k,t}}{\alpha_{k,t} + \beta_{k,t}} = \frac{\mbox{\#Successes} +	
	\alpha_{k,0}}{\mbox{\#Trials}+\alpha_{k,0}+\beta_{k,0}}.
\end{align*}

@@

Continuous Correlated Beta Processes(CCBPs) were introduced by Goetschalckx et al.~\cite{} to model correlations between the Bernoulli random variables in a Beta-Bernoulli process, which may lead to faster convergence in Multi-Armed Bandit problems~\cite{}.
Such correlations may exist when the Bernoulli random variables depend on common latent factors.
For example, two probability of force closure variables $\theta_k$ may be correlated when two grasps have similar poses or when the surface geometry near the points at which they contact an object are similar.

A CCBP is a Beta-Bernoulli process with an additional parameter $k(g_i, g_j) : \mathcal{G} \times \mathcal{G} \rightarrow [0,1]$, called the kernel, that measures similarity between two grasps.
The kernel should approach 1 as the arguments become increasingly similar and approach 0 as the arguments become dissimilar.
Let $F_{1}(g_{I(1)}), ..., F_{t}(g_{I(t)})$ be $t$ observations of force closure from samples of our uncertainty models for grasps $g_{I(1)}, ..., g_{I(t)}$, where $I(j)$ is the index of the grasp sampled at time $j$.
Then the CCBP posterior update for $\theta_k$ is~\cite{}:

\vspace{-2ex}
\begin{align*}
	p \left(\theta_k | F_{1}(g_{I(1)}), ..., F_{t}(g_{I(t)}) \right) &= \betadist\left( \alpha_{k,t}, \beta_{k,t} \right) \\
	\alpha_{k,t} &= \alpha_{k,0} + \sum \limits_{j=1}^t k(g_k, g_{I(j)}) F_{i}(g_{I(j)}) \\
	\beta_{k,t} &= \beta_{k,0} + \sum \limits_{=1}^t k(g_k, g_{I(j)}) (1 - F_{i}(g_{I(j)}))
\end{align*}

\noindent Therefore grasps can constitute "effective" observations of other grasps if the two grasps are similar according to the kernel function.

>>>>

Finding an approximate solution of Equation~\ref{eq:objective} using Multi-Armed Bandits requires a model of the reward distribution of each arm.
We use Continuous Correlated Beta Processes (CCBPs) to model the probability of force closure of grasps as a Bernoulli random variable with correlations between grasps.
We refer the reader to Goetschalckx et al.~\cite{} for a detaled description of CCBPs.
In practice, correlations may occur between grasps that contact the shape in similar locations may have similar probabilities of force closure.
Correlations may also occur between grasps on different shapes, such as grasping the handle of a mug and the handle of a teapot.

@@

For clarity we first review Beta-Bernoulli Processes, the uncorrelated version of CCBPs. 
Let $\Gamma = \{g_k\}_{k=1}^K$ denote our discrete set of $K$ candidate grasps.
Let $F(\bg_k) \in \{0, 1\}$ denote the occurence of force closure for a grasp $\bg_k$.
We model $F(\bg_k)$ as a Bernoulli random variable with probability of success $\theta_k = P_F(\bg_k)$.
Since we do not know the value of $\theta_k$ for each grasp, we can specify a distribution of $\theta_k$ based on our prior belief about the likelihood of force closure.
A common choice for a prior on the Bernoulli parameter $\theta_k$ is the Beta distribution, which is specified by shape parameters $\alpha > 0$ and $\beta > 0$:

@@

\begin{align*}
	\mathbb{E} \left[ \theta_k | F_{1}(g_k), ..., F_{t}(g_k) \right] &= \frac{\alpha_{k,t}}{\alpha_{k,t} + \beta_{k,t}} \\
	&= \frac{\mbox{\#Successes} +	
	\alpha_{k,0}}{\mbox{\#Trials}+\alpha_{k,0}+\beta_{k,0}}.
\end{align*}

@@

Continuous Correlated Beta Processes(CCBPs) were independently developed by Goetschalckx et al.~\cite{goetschalckx2011continuous} and Montesano and Lopes~\cite{montesano2012active} to model correlations between the Bernoulli random variables in a Beta-Bernoulli process, which may lead to faster convergence in Multi-Armed Bandit problems~\cite{chu2011contextual}.
Such correlations may exist when the Bernoulli random variables depend on common latent factors.
For example, two probability of force closure variables $\theta_k$ may be correlated when two grasps have similar poses or when the surface geometry near the points at which they contact an object are similar.

A CCBP is a Beta-Bernoulli process with an additional parameter $k(\bg_i, \bg_j) : \mathcal{G} \times \mathcal{G} \rightarrow [0,1]$, called the kernel, that measures similarity between two grasps.
The kernel approaches 1 as the arguments become increasingly similar and approaches 0 as the arguments become dissimilar.
One common choice of kernel is the squared exponential kernel 
\begin{align*}
	k(\bg_i, \bg_j) &= \exp\left( -d(\bg_i, \bg_j)^2 \right)
\end{align*}
\noindent where $d(\cdot): \mathcal{G} \times \mathcal{G} \rightarrow \mathbb{R}_{+}$ is a distance metric between grasps.
A common choice of distance metric is
\begin{align*}
	d(\bg_i, \bg_j) &= \left( \phi(\bg_i) - \phi(\bg_j) \right)^T C^{-1} \left( \phi(\bg_i) - \phi(\bg_j)\right)
\end{align*}
\noindent where $\phi(\cdot) : \mG \rightarrow \mathbb{R}^m$ is an $m$-dimensional feature representation of grasps and $C \in \mathbb{R}^{m \times m}$ is the {\it kernel bandwidth}.
The bandwidth $C$ scales dimensions of the feature space to mark some dimensions as being more or less relevant for measuring similarity between grasps.

Given a kernel, on each observation we update the belief of each grasp proportional to how similar it is to the observed grasp as measured by the kernel. 
Let $F_{1}(\bg_{I(1)}), ..., F_{t}(\bg_{I(t)})$ be $t$ observations of force closure from samples of our uncertainty models for grasps $g_{I(1)}, ..., g_{I(t)}$, where $I(j)$ is the index of the grasp sampled at time $j$.
Then the CCBP posterior update for $\theta_k$ is~\cite{}:

\vspace{-2ex}
\begin{align*}
	p \left(\theta_k | F_{1}(g_{I(1)}), ..., F_{t}(g_{I(t)}) \right) &= \betadist\left( \alpha_{k,t}, \beta_{k,t} \right) \\
	\alpha_{k,t} = \alpha_{k,0} + \sum \limits_{j=1}^t k(g_k, g_{I(j)}) F_{i}(g_{I(j)}) \\
	\beta_{k,t} = \beta_{k,0} + \sum \limits_{=1}^t k(g_k, g_{I(j)}) (1 - F_{i}(g_{I(j)}))
\end{align*}

\noindent Intuitively, this allows observations of a grasp to constitute "effective" observations of other grasps.

### 2015-07-27 ICRA2016/bandits_docs/includes/problem_statement.tex
Updated the correlated bandits paper with detailed related work, references, a revised intro problem statement, and background, and added some todos. Long way to go

Let $g \in \mathfrak{se}(3)$ denote an attempted pose of the robot end-effector in 3D space, and $\Gamma = \{ g_1, ..., g_N\}$ denote a set of candidate grasps.
Let $\upsilon$ denote uncertainty in object shape represented by a Gaussian Process implicit surface~\cite{} distribution over signed distance fields $f$ with mean $\mu_f \in \mathbb{R}^{M \times M}$ and covariance $\Sigma_f$.
Let $\xi$ denote Gaussian uncertainty in object pose with mean $\mu_{\xi} \in \mathfrak{se}(3)$ and covariance $\Sigma_{\xi}$.
Let $\rho$ denote Gaussian uncertainty in gripper pose with mean $\mu_{\rho} \in \mathfrak{se}(3)$ and covariance $\Sigma_{\rho}$.
Let $\zeta$ denote Gaussian uncertiainty in friction coefficient mean $\mu_{\zeta} \in \mathbb{R}$ and covariance $\Sigma_{\zeta}$.

We are interested in finding the candidate grasp that maximizes the probability of force closure $P_F(g) = \mathbb{P} \left( F = 1 \big| g, \upsilon, \xi, \rho, \zeta\right)$~\cite{} subject to these sources of uncertainty over a budgeted maximum number of samples $T$.
To perform this as q	uickly as possible we formulate this as a maximization over the sum of $P_F$ for the grasps sampled at iteration $t$.

\vspace{-2ex}
\begin{align*}
	\maximum{g_1, ..., g_T \in \Gamma} \sum \limits_{t=1}^T P_F(g_{t})
\end{align*}

\noindent Laskey et al.~\cite{} proposed to solve this objective using algorithms for Multi-Armed Bandits.
In this work, we propose to use Multi-Armed Bandits with correlations between arms to further accelerate convergence.

>>>>

\TODO{Fill in more details. This is a stripped down version to get ideas down on the page}
Let $\bg = [\bx, \bw]^T$ be a parallel-jaw grasp parameterized by its center in 3D space $\bx \in \mathbb{R}^3$ and approach direction $\bv \in \mS^2$.
Let $\mG = \{ [\bx, \bw]^T \big| \bx \in \mathbb{R}^3,  \}$ denote the space of all grasps.
%We will assume a fixed set of candidate grasps $\Gamma = \{ g_1, ..., g_N\}$.
%Ideally the candidate set would form a cover of the which may be generated via Gaussian pose sampling~\cite{} or heur.

We will assume a known object shape $\nu$, and known uncertainty in object pose, gripper pose, and friction coefficient resulting from sensing uncertainties and missing data following the model of Laskey et al.~\cite{laskey2015bandits}. 
%Let $\upsilon$ be a random variable representing object shape represented by a Gaussian Process implicit surface~\cite{} distribution over signed distance fields $f$ with mean $\mu_f \in \mathbb{R}^{M \times M}$ and covariance $\Sigma_f$.
Let $\xi$ be uncertainty in object pose distributed as a Gaussian with mean $\mu_{\xi} \in \mathfrak{se}(3)$ and covariance $\Sigma_{\xi}$.
Let $\rho$ be uncertainty in gripper pose distributed as a Gaussian with mean $\mu_{\rho} \in \mG$ and covariance $\Sigma_{\rho}$.
Let $\zeta$ denote uncertiainty in friction coefficient distributed as a Gaussian with mean $\mu_{\zeta} \in \mathbb{R}$ and covariance $\Sigma_{\zeta}$.
Given object shape and samples of object pose, and gripper pose, we let $\bc_i(\bg, \theta, \xi, \rho) \in \mathbb{R}^3$ for $i \in {1, 2}$ denote the 3D location of contact between the $i$-th gripper jaw and surface.
Furthermore, let $\bn_i(\bc_i, \nu) \in \mS^2$ denote the surface normal at this contact.
A graphical model describing the relationship between these quantities is given in~\figref{graphical-model}.

We measure grasp quality by the probability of force closure subject to these uncertain quantities.
Let $F \in \{0, 1\}$ denote the occurence of force closure, or the ability to resist wrenches in arbitrary directions~\cite{ferrari1992}.
Then the probability of force closure for a grasp $\bg$ is
%\vspace{-2ex}
\begin{align*}
	P_F(\bg) = \mathbb{P}\left(F = 1 \mid \bg, \xi, \rho, \zeta \right).
\end{align*}
\noindent We are interested in finding the candidate grasp that maximizes the probability of force closure $P_F(g)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} subject to these sources of uncertainty over a budgeted maximum number of samples $T$.
To perform this as q	uickly as possible we formulate this as a maximization over the sum of the true $P_F$ for the grasps sampled at iteration $t$, where $I(i)$ denotes the grasp selected at time $t$

\vspace{-2ex}
\begin{align}
	\maximum{g_{I(1)}, ..., g_{I(T)} \in \mG} \sum \limits_{t=1}^T P_F(g_{I(t)}) \label{eq:objective}
\end{align}

\noindent As the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective using a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$.
In practice $\Gamma$ has been set using Gaussian sampling of grasp centers and poses~\cite{laskey2015bandits} or using heuristics such as antipodality~\cite{mahler2015opt}.
\TODO{Switch to task-based quality metric (e.g. resiting gravity)? I think it would be more compelling but doesn't seem to have much precedent}

Even with a discrete set of candidates, evaluating $P_F(\bg)$ for any grasp requires an expensive integration over possible contact locations between the grasp and surface and the surface normals at these contacts~\cite{mahler2015gp}.
Thus, past work has evaluated the probability of force closure using Monte-Carlo integration~\cite{kehoe2012estimating, kehoe2012toward, weisz2012pose}, approximating the expression by minimzing uncertainty at the contact locations~\cite{mahler2015gp}, and using Multi-Armed Bandit algorithms to jointly evaluate $P_F(\bg)$ using Monte-Carlo integration while allocating samples to more promising grasps.
In this work, we propose to use Multi-Armed Bandits with correlations between arms to further accelerate convergence.

### 2015-07-27 ICRA2016/bandits_docs/includes/related_work.tex
Updated the correlated bandits paper with detailed related work, references, a revised intro problem statement, and background, and added some todos. Long way to go

Many works on grasp planning focus on finding grasps by maximizing a grasp quality metric, such as the ability to resist external perturbations to the object in wrench space~\cite{ferrari1992, miller2004graspit}.
These metrics have been used to synthesize grasps for known objects using sampling-based optimization in software tools such as GraspIt!~\cite{miller2004graspit} or OpenGRASP~\cite{}.
However, analytic grasp quality metrics have been criticized for relying on perfect knowledge of object shape, pose, material properties, and locations of contact~\cite{cheong2011output} and the abliity of a gripper to actuate any contact force in the friction cone, which is not true of many real-world grippers~\cite{}.
Recent work has also suggested that grasp closure metrics may fail to accurately predict of grasp success on a physical robot~\cite{balasubmaranian, weisz}.
This has motivated work on transferring known grasps from a database to new objects, evaluating robust versions of analytic quality metrics with respect to uncertainty in the state of the robot and environment, and work on data-driven grasp synthesis~\cite{}.

Many works have approached grasp synthesis for unknown or familiar objects by transferring grasps from a benchmark set of exemplar objects in a large database.
%Ciocarlie et al.~\cite{ciocarlie2009} found that human hand postures lie on a low-dimensional subspace, called eigen-grasps, and exploited this structure to speed up grasp optimization to synthesize grasps at a large scale in GraspIt!.
Li and Pollard~\cite{} generated grasps by matching object shapes to human hand postured in a database.
Hillebrand and Roa~\cite{} transfer grasps from objects of the same category using pose alignment and geometric warping betwen corresponding points on a shape surface.
Goldfelder et al.~\cite{} developed the Columbia grasp database, a database of 1,814 distinct models and over 200,000 form closure grasps generated using the Eigengrasp planner in GraspIt!~\cite{ciocarlie2009}.
The authors later used synthetic partial depth maps of objects in the database to match robot sensor data to precomputed grasps, using the Iterated Closest Point (ICP) algorithm to align the coordinate frames of the depth maps~\cite{partial}.
Detry et al.~\cite{91inbohg} create a low-dimensional representation of object parts and cluster object parts that are grasped similarly to form a shape library of prototypical grasp parts, and show that this representation can be transferred to real sensor data~\cite{}.

Work on evaluating grasp quality metrics under uncertainty, such as the probability of force closure, has considered uncertainty in the state of a robotic gripper~\cite{goldberg1990bayesian, stulp2011learning} and uncertainty in contact locations with an object~\cite{zheng2005}.
Recent work has also studied the effects of uncertainty in object pose and gripper positioning~\cite{brook2011collaborative, hsiao2011bayesian}.
Brook, Ciocarlie, and Hsiao~\cite{brook2011collaborative, hsiao2011bayesian} studied a Bayesian framework to evaluate the probability of grasp success given uncertainty in object identity, gripper positioning, and pose by simulating grasps on deterministic mesh and point cloud models.
Weisz et al.~\cite{weisz2012pose} and Kim et al.~\cite{kim2012physically} independently found that grasps ranked by probability of force closure subject to perturbations of object pose in simulation were empirically more successful on a physical robot than grasps planned using deterministic wrench space metrics. 
Many works have also studied grasping under object shape uncertainty resulting from imprecision of object segmentations in images~\cite{chris}, part tolerancing in manufacturing~\cite{kehoe}, or missing and noisy data from depth sensors such as the Kinect~\cite{mahler, laskey}.
Many have also studied caging gripper configurations, which may be a waypoint to form closure grasps and are robust to perturbations in object pose and shape~\cite{}.

Another approach for synthesizing grasps on objects is to sample grasps and rank them according to metrics derived from human labels or physical execution~\cite{bohg}.
Saxena et al.~\cite{bothsaxenaworks} used a logistic regression classified to predict grasp afordances in images from human annotated training data.
Several other works have examined predicting grasp points using depth gradient features~\cite{rao}, global shape context descriptors~\cite{}, and 3D edges~\cite{}. 
Lenz et al~\cite{lenz} used deep learning to detect grasp bounding boxes in color and depth images.
Herzog et al.~\cite{} extract "heightmaps" of local object curvature from human demonstrated grasps, construct a library of heightmap templates, and match new sensor data to templates to select grasps similar to the demonstrations.
Kappler et al.~\cite{} trained a deep neural network to predict human labelled grasps for a Barett hand on a database of synthetic objects.
Recently, several works have studied forming a database of grasps on synthetic objects from simulation outcomes~\cite{detry} or physical execution~\cite{tellex}.
In comparison, our work uses data-driven correlations between grasps based on local and global features of an object surface to quickly and adaptively acquire samples for evaluating and ranking grasps by their likelihood of success.

Active learning for grasp planning is an active area of research.
Several works have studied active search for successful grasps by minimzing uncertainty about the state of the envirnoment~\cite{kahn, vincsze}, but without use of an explicit grasp quality metric to guide the search.
Recently, Laskey et al.~\cite{} showed that MAB algorithms can be used to accelerate the identification of a grasp with high probability of force closure under uncertainty in shape, pose, and friction in 2D.
Tellex et al.~\cite{} proposed an initiative to adaptively collect a dataset of grasps and point clouds for one million objects using MAB and reinforcemen learning.
MAB algorithms select the next grasp to sample by trading off gaining information about grasps with few samples and exploiting the success of grasps known to work well.
In robotics, MAB algorithms have also been for speeding up probabilistic roadmap motion planning by adaptively sampling waypoints~\cite{hsu2005hybrid}, searching for the best state machine for a particular task~\cite{matikainen2013multi}, solving mixed observable POMDPs~\cite{Mikko2015POMDP}, and multi-agent navigation~\cite{guy}.

One shortcoming of the MAB model used by Laskey et al. is that it did not take into account correlations between grasps~\cite{}.
In reality, grasp correlations may occure from grasps with similar poses~\cite{}, objects with similar global structure~\cite{}, or on surfaces with similar local geometry~\cite{}.
Correlated Multi-Armed Bandit (CMAB) models, also referred to as Bayesian Optimization models~\cite{}, have been used to trading off infromation gathering and exploitation in applicatoins such as ad-serving~\cite{}, next-best view prediction in object modeling~\cite{}, envrionmental monitoring in robotics~\cite{}.
Perhaps the most common model of correlations in a CMAB is a linear model~\cite{}, however this depends on the selection of features are linearly related to a success criteria.
Another common model of correlations is a Gaussian Process (GP)~\cite{}, which can model nonlinear relationships between options and rewards but are expensive to update with new observations ($O(n^2)$ where $n$ is the number of observations so far).
As a result, several fast approximate version of GP bandit algorithms exist, such as local GPs~\cite{} and hierarchical GPs~\cite{}.
Recently, Goetschalckx et al.~\cite{} developed the Continuous Correlated Beta Process (CCBP), a nonlinear model of 0-1 reward probabilities.
CCBPs are inexpensive to update compared to GPs, requiring $O(n)$ time in the worst case and a much smaller factor when efficient nearest neighbor queries can be performed~\cite{}.
In this work we utilize CCBPs to model correaltions between grasps because of their ability to scale to thousands of grasp observations with reasonable runtime.

>>>>

Many works on grasp planning focus on finding grasps by maximizing a grasp quality metric, such as the ability to resist external perturbations to the object in wrench space~\cite{ferrari1992, miller2004graspit}.
These metrics have been used to synthesize grasps for known objects using sampling-based optimization in software tools such as GraspIt!~\cite{miller2004graspit} or OpenGRASP~\cite{leon2010opengrasp}.
However, analytic grasp quality metrics have been criticized for relying on perfect knowledge of object shape, pose, material properties, and locations of contact~\cite{cheong2011output, diankov2010automated, weisz2012pose, zheng2005} and for not taking into account the dynamics of the the grasp~\cite{bicchi2000robotic, prattichizzo2008grasping}.
Recent work has also suggested that grasp closure metrics may fail to accurately predict of grasp success on a physical robot~\cite{balasubramanian2012physical, weisz2012pose}.
This has motivated work on transferring known grasps from a database to new objects, evaluating robust versions of analytic quality metrics with respect to uncertainty in the state of the robot and environment, and work on data-driven grasp synthesis.

Many works have approached grasp synthesis for unknown or familiar objects by transferring grasps from a benchmark set of exemplar objects in a large database.
%Ciocarlie et al.~\cite{ciocarlie2009} found that human hand postures lie on a low-dimensional subspace, called eigen-grasps, and exploited this structure to speed up grasp optimization to synthesize grasps at a large scale in GraspIt!.
Li and Pollard~\cite{li2005shape} generated grasps by matching object shapes to human hand postured in a database.
Goldfelder et al.~\cite{goldfeder2009columbia} developed the Columbia grasp database, a database of 1,814 distinct models and over 200,000 form closure grasps generated using the Eigengrasp planner in GraspIt!~\cite{ciocarlie2009}.
The authors later used synthetic partial depth maps of objects in the database to match robot sensor data to precomputed grasps, using the Iterated Closest Point (ICP) algorithm to align the coordinate frames of the depth maps~\cite{goldfeder2009data, goldfeder2011data}.
Several works have also transferred grasps from objects of the same category by warping contacts betwen corresponding points on a shape surface and locally replanning using local rigid alignment and contact interpolation~\cite{hillenbrand2012transferring, stouraitis2015functional} or by interpolating a shape and grasp over a Grasp Moduli Space~\cite{pokorny2013grasp, pokorny2014grasp}.
Detry et al.~\cite{detry2012generalizing} create a low-dimensional representation of object parts and cluster object parts that are grasped similarly to form a shape library of prototypical grasp parts, and show that this representation can be transferred to real sensor data~\cite{detry2013learning}.

Work on evaluating grasp quality metrics under uncertainty, such as the probability of force closure, has considered uncertainty in the state of a robotic gripper~\cite{goldberg1990bayesian, stulp2011learning} and uncertainty in contact locations with an object~\cite{zheng2005}.
Recent work has also studied the effects of uncertainty in object pose and gripper positioning~\cite{brook2011collaborative, hsiao2011bayesian}.
Brook, Ciocarlie, and Hsiao~\cite{brook2011collaborative, hsiao2011bayesian} studied a Bayesian framework to evaluate the probability of grasp success given uncertainty in object identity, gripper positioning, and pose by simulating grasps on deterministic mesh and point cloud models.
Weisz et al.~\cite{weisz2012pose} and Kim et al.~\cite{kim2012physically} independently found that grasps ranked by probability of force closure subject to perturbations of object pose in simulation were empirically more successful on a physical robot than grasps planned using deterministic wrench space metrics. 
Many works have also studied grasping under object shape uncertainty resulting from imprecision of object segmentations in images~\cite{christopoulos2007handling}, part tolerancing in manufacturing~\cite{kehoe2012estimating, kehoe2012toward}, or missing and noisy data from depth sensors such as the Kinect modeled with Gaussian process implicit surfaces~\cite{mahler2015gp, laskey2015bandits}.
Many have also studied caging gripper configurations~\cite{rimon1996caging}, which are a waypoint to form closure grasps for two fingers~\cite{vahedi2008caging, rodriguez2012caging} and may be robust to perturbations in object pose and shape~\cite{diankov2008manipulation, Wan2012_ICRA}.

Another approach for synthesizing grasps on objects is to sample grasps and rank them according to metrics derived from human labels or physical execution~\cite{bohg2014data}.
Saxena et al.~\cite{jiang2011efficient, saxena2008robotic} used a logistic regression classified to predict grasp afordances in images from human annotated training data.
Several other works have examined predicting grasp points using depth edges~\cite{rao2010grasping}, combinations of 2D and 3D edges~\cite{le2010learning}, and global shape descriptors~\cite{bohg2010learning}. 
Lenz et al~\cite{lenz2015deep} used deep learning to detect grasp bounding boxes in color and depth images, which was later extended to real time by Redmon and Angelova~\cite{redmon2014real}.
Many works have also considered predicting grasp success from 3D point clouds.
Herzog et al.~\cite{herzog2012template, herzog2014learning} extract "heightmaps" of local object curvature from human demonstrated grasps, construct a library of heightmap templates, and match new sensor data to templates to select grasps similar to the demonstrations.
Kappler et al.~\cite{kappler2015leveraging} trained a deep neural network to predict human labelled grasps for a Barett hand on a database of synthetic pointclouds of objects.
Recently, several other works have proposed to form a huge database of grasps on synthetic objects from simulation outcomes~\cite{michalikg3db} or physical execution~\cite{tellex}.
In comparison, our work studies the convergence rate for adaptively acquiring samples for evaluating and ranking grasps by their likelihood of success through the use of data-driven grasp correlations based on local and global features of an object surface.

Many works have also considered using data-driven approaches for actively selecting grasps.
Several works have studied active search for successful grasps by minimzing uncertainty about the state of the envirnoment~\cite{hsiao2007grasping, kahnactive, fischinger2015learning}, but without use of an explicit grasp quality metric to guide the search.
Kehoe et al.~\cite{kehoe2012estimating} proposed iterative pruning, an algorithm for evaluating the probability of force closure for a set of candidate grasps while discrading grasps known to have poor quality.
Tellex et al.~\cite{} proposed an initiative to adaptively collect a dataset of grasps and point clouds for one million objects using MAB and reinforcemen learning.
Detry et al.~\cite{detry2011learning} estimated a full continuous density function over grasp poses using kernel density estimation and adaptively acquired samples by pruning unsuccessful grasps.
Recently, Laskey et al.~\cite{laskey2015bandits} showed that Multi-Armed Bandit algorithms can be used to accelerate the identification of grasps with high probability of force closure under uncertainty in shape, pose, and friction in 2D over candidate sets of 1,000 grasps on 88 objects. 
MAB algorithms select the next grasp to sample by trading off gaining information about grasps with few samples and exploiting the success of grasps known to work well.
In robotics, MAB algorithms have also been for speeding up probabilistic roadmap motion planning by adaptively sampling waypoints~\cite{hsu2005hybrid}, searching for the best state machine for a particular task~\cite{matikainen2013multi}, solving mixed observable POMDPs~\cite{Mikko2015POMDP}, and multi-agent navigation~\cite{godoy2015adaptive}.

One shortcoming of the MAB model used by Laskey et al. is that it did not take into account correlations between grasps~\cite{laskey2015bandits}.
In reality, grasp correlations may occur from grasps with similar configurations~\cite{ciocarlie2009, detry2011learning}, objects with similar global structure~\cite{pokorny2013grasp}, or on point cloud surfaces with similar local geometry~\cite{boularias2011learning, herzog2012template, kroemer2010combining, saxena2008robotic}.
Correlated Multi-Armed Bandit (CMAB) models, sometimes also referred to as Bayesian Optimization models~\cite{brochu2010tutorial}, have been used to trading off infromation gathering and exploitation in applicatoins such as ad-serving~\cite{chu2011contextual} and envrionmental monitoring in robotics~\cite{hitz2014fully, marchant2012bayesian}.
Perhaps the most common model of correlations in a CMAB is a linear model~\cite{chu2011contextual}, however this depends on the selection of features are linearly related to a success criteria.
Another common model of correlations is a Gaussian Process (GP)~\cite{rasmussen2006}, which can model nonlinear relationships between options and rewards.
Kroemer et al.~\cite{kroemer2010combining} developed a reinforcement learning approach to grasp selection based on seeding hypothesse via imitation learning and Gaussian process upper-confidence bounds to predict grasp successeses and determine the next grasp to select.
Boularias et al.~\cite{boularias2014efficient} used a Gaussian process Bayesian Optimization model for selecting grasps on cluttered piles of rocks. 
However, GP models are expensive to update with new observations ($O(n^2)$ where $n$ is the number of observations so far)~\cite{rasmussen2006}, which limited the scale of experiments in both simulation and the physical world that the authors could perform.
To make the model more tractable, Boularias et al. later extended their work to use an heuristic upper confidence bound-based reinforcement learning~\cite{boularias2015learning}.
Recently, Goetschalckx et al.~\cite{goetschalckx2011continuous} developed the Continuous Correlated Beta Process (CCBP), a nonlinear model of 0-1 reward probabilities.
CCBPs are inexpensive to update compared to GPs, requiring $O(n)$ time in the worst case and a much smaller factor when efficient nearest neighbor queries can be performed~\cite{goetschalckx2011continuous}.
Montesano and Lopes~\cite{montesano2012active} used CCBPs (although the authors did not refer to them as CCBPs) to actively acquire grasp executions, measuring correlations from the responses to a bank of 151 image filters.
In this work we also utilize CCBPs to model correaltions between grasps, and study their performance on grasping simulations over thousands of objects.
